---
title: "Untitled"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
Model between the response and neither of the explanatory variables 
```{r cars}
heart_2%>%
  ggplot(aes(x=RestingBP))+ geom_histogram()
```

- Model between the response and the numerical explanatory variable  
Resting BP= 105.69194+0.50176(Age)
```{r}
base_model1<-lm(RestingBP~Age, data=heart_2)
summary(base_model1)

ggplot(data=heart_2, aes(x=Age, y=RestingBP))+geom_point()+ geom_smooth(method="lm", se=F)

```
- Model between the response and the categorical explanatory variable   
RestingBP = 130.1805 + 4.2692(HeartDisease)

```{r pressure, echo=FALSE}
base_model2<-lm(RestingBP~HeartDisease, data=heart_2)
summary(base_model2)
ggplot(data=heart_2, aes(x=HeartDisease, y=RestingBP))+geom_jitter()+geom_abline(aes(slope=4.2692, intercept=130.1805))
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
